### 2019-06-03 03_problem.tex
tase initial update

\begin{wrapfigure}{r}{2.4in}
    \vspace{-.3in}
	\centering
	\includegraphics[width=1.115in,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_start}
	\includegraphics[width=1.115in,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_end}
    \vspace{-.15in}
	\caption{An example of object rearrangement involving two robotic arms. Initial (left) and final (right) object configuration.}
	\label{fig:rearrangement}
    \vspace{-.35in}
\end{wrapfigure}
Two robot arms $\arm^1$ and $\arm^2$ can 
% pick, raise above the surface and place the objects. 
pick and place the objects from and to the surface.
% \kiril{The last statement is unclear, particularly the purpose of the word "raise". Can it be rewritten into "...can pick and place objects from and to the surface."?}  
% THE OLD SENTENCE$\cfree^k$ is the set of collision-free configurations for arm $ \arm^k $, where $ q^k \in \cfree^k %\subset \reals^d $ (while ignoring possible collisions with  objects or the other arm).
$\cfree^k$ is the set of collision-free configurations for arm $\arm^k$ (while ignoring possible collisions with  objects or the other arm), and is assumed here to be a subset of $\reals^d $.
A path for $\arm^k$ is denoted as $ \pi^k : [0,1] \rightarrow \cfree^k$ and includes picking and placing actions.  Let $ \cfree^i(\pi^j) $ represent the collision free $\mathbb{C}$-space for $\arm^i$, given that $\arm^j$ moves along $\pi^j $. This is a function of the paths' parametrization. The space of dual-arm paths $\mathcal{D}$ denotes pairs of paths for the two arms: $D = (\pi^1,\pi^2) \in \mathcal{D}$. Then, $\arrangement(\ainit, D)$ is the resulting arrangement when the objects are at $\ainit$ and moved according to $D$.   Let $ \cost(D) : \mathcal{D} \rightarrow \reals $ be a cost function over dual-arm paths.

\vspace{-.1in}
{\definition [Optimal Dual-arm Rearrangement] Given arms $\arm^1$, $\arm^2$ and objects $\objectset$ to be moved from initial arrangement $ \ainit \in \Afree$ to target arrangement $ \atarget \in \Afree $, the optimal dual-arm rearrangement problem asks for a dual-arm path $D^* \in \mathcal{D}$, which satisfies the following constraint:

\vspace{-.15in} 
\begin{equation}
D^* =  (\pi^{*1}, \pi^{*2}) \ |\ \arrangement(\ainit, D^*) = \atarget \textrm{ and } \pi^{*i} \in \cfree^i(\pi^{*j}) \vspace{-.05in}
\label{eq:dualarm_constraint}
\end{equation}
\noindent and optimizes a cost function: $D^* = \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} } \ \cost(D).$}

@@

\vspace{-.15in}
{\assumption [Monotonicity] There are dual-arm paths $D = (\pi^1,\pi^2)$ that satisfy Eq. \ref{eq:dualarm_constraint}, where each object $ \object_i \in \objectset $ appears once in $\moveset(\pi^1)$ or $ \moveset(\pi^2)$.}

@@

\vspace{-.1in}
{\assumption [Synchronicity] Consider dual-arm paths, which can be decomposed into a sequence of simultaneous transfers and moves for both arms:
\vspace{-.1in}
\begin{equation}
D=\left(T(\pi^1_1,\pi^2_1),M(\pi^1_{1\rightarrow 2},\pi^2_{1\rightarrow 2}), \ldots , M(\pi^1_{\ell-1\rightarrow \ell},\pi^2_{\ell-1\rightarrow \ell}), T(\pi^1_\ell,\pi^2_\ell)\right).\vspace{-.05in}
\label{eq:synchronicity}
\end{equation}}
\noindent For simplicity, Eq.~\ref{eq:synchronicity} does not include an initial move from $q^k_{\rm safe} \in \cfree^k$ and a final move back to $q^k_{\rm safe}$. An odd number of objects can also be easily handled. Then, the sequence of object pairs moved during a dual-arm path as in Eq. \ref{eq:synchronicity} is: \vspace{-.1in} 
% $$ \scoma(D) = \left(  \coma_i = (\object_i^1,\object_i^2) \ |\ i,j\in [1,\cdots,\ell], \bigcup_i (\object_i^1 \cup \object_i^2) = \objectset, \object_i^1 \cap \object_j^1 = \object_i^2 \cap \object_j^2 = \emptyset \right). \vspace{-.15in}$$
$$ \scoma(D) = \left(  \coma_i = (\object_i^1,\object_i^2) \ |\ i,j\in [1\cdots \ell], \bigcup_i (\object_i^1 \cup \object_i^2) = \objectset, \forall k,k'\in[1,2], \object_i^k \neq \object_j^{k'} \right). \vspace{-.1in}$$

@@

\vspace{-.1in}
{\assumption [Object Non-Interactivity] There are collision-free transfers $T(\coma_i)$ and moves $M(\coma_{i\rightarrow i^{\prime}})$ regardless of the object poses in $\ainit$ and $\atarget$.}
\commentadd{This entails that there is no interaction between the $n$ resting objects and the arms during transits. Similarly, there are no interactions between the arm-object system and the $n-2$ resting objects during the transfers. Collisions involving the arms, static obstacles and picked objects are always considered.}
\commentdel{
This assumption is valid in tabletop setups where the arms can raise the picked objects above the resting surface. 
% Furthermore, this assumption implies that transfers and moves involving object poses in $\ainit, \atarget$ are always feasible and the challenge is deciding the appropriate sequence of object-to-arm assignments.
This assumption lets the study focus on the challenge of deciding the appropriate sequence of object-to-arm assignments.
}

The metric this work focuses on relates to makespan and minimizes the sum of the longest distances traveled by the arms in each synchronized operation. Let $ \| \pi^k \| $ denote the Euclidean arc length in $\cfree^k  \subset \reals^d$ of path $ \pi^k $. Then, for transfers $\cost( T(\pi^1_i,\pi^2_i) ) = \max\{ \|\pi^1_i\|, \|\pi^2_i\| \}$. Similarly, $\cost( M(\pi^1_{i\rightarrow i^{\prime}},\pi^2_{i\rightarrow i^{\prime}}) ) = \max\{ \|\pi^1_{i\rightarrow i'}\|, \|\pi^2_{i\rightarrow i'}\| \}$. Then, over the entire dual-arm path $ \D $ define:
\vspace{-.15in}
\begin{equation}
\cost(\D) 
% = \cost_{ T} + \cost_{ M} 
= \sum_{i=1}^{\ell}   \cost(T(\coma_i))   + \sum_{i=1}^{\ell-1}   \cost(M(\coma_{i\rightarrow i+1})). 
\vspace{-.1in}
\label{eq:cost_function}
\end{equation}
Note that the \textit{transfer} costs do not depend on the order with which the objects are moved but only on the assignment of objects to arms. The \textit{transit} costs arise out of the specific ordering in $ \scoma(D)$. 
Then, for the setup of Definition 1 and under Assumptions 1-3, the problem is to compute the optimal sequence of object pairs $\scoma^*$ so that $D(\scoma^*)$ satisfies Eq.~\ref{eq:dualarm_constraint} and minimizes the cost of Eq.~\ref{eq:cost_function}.

@@

\commentadd{
\noindent \textbf{Note on Assumptions:} This work restricts the study to a class of monotone problems that relate to a range of industrial packing and stowing applications. The monotonicity assumption is often used in manageable variants of well-studied problems~\cite{Wilson:1994fk,Halperin:2000uq}. A monotone solution also implies that every object's start and target is reachable by at least one arm. To deal with cases where the number of reachable objects is unbalanced between the two arms, a {\tt NO\_ACT} task assignment is introduced and considered in Section 6.

>>>>

\begin{wrapfigure}{r}{2.4in}
    % \vspace{-.3in}
	\centering
	\includegraphics[width=1.115in,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_start}
	\includegraphics[width=1.115in,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_end}
    % \vspace{-.15in}
	\caption{An example of object rearrangement involving two robotic arms. Initial (left) and final (right) object configuration.}
	\label{fig:rearrangement}
    % \vspace{-.35in}
\end{wrapfigure}
Two robot arms $\arm^1$ and $\arm^2$ can 
% pick, raise above the surface and place the objects. 
pick and place the objects from and to the surface.
% \kiril{The last statement is unclear, particularly the purpose of the word "raise". Can it be rewritten into "...can pick and place objects from and to the surface."?}  
% THE OLD SENTENCE$\cfree^k$ is the set of collision-free configurations for arm $ \arm^k $, where $ q^k \in \cfree^k %\subset \reals^d $ (while ignoring possible collisions with  objects or the other arm).
$\cfree^k$ is the set of collision-free configurations for arm $\arm^k$ (while ignoring possible collisions with  objects or the other arm), and is assumed here to be a subset of $\reals^d $.
A path for $\arm^k$ is denoted as $ \pi^k : [0,1] \rightarrow \cfree^k$ and includes picking and placing actions.  Let $ \cfree^i(\pi^j) $ represent the collision free $\mathbb{C}$-space for $\arm^i$, given that $\arm^j$ moves along $\pi^j $. This is a function of the paths' parametrization. The space of dual-arm paths $\mathcal{D}$ denotes pairs of paths for the two arms: $D = (\pi^1,\pi^2) \in \mathcal{D}$. Then, $\arrangement(\ainit, D)$ is the resulting arrangement when the objects are at $\ainit$ and moved according to $D$.   Let $ \cost(D) : \mathcal{D} \rightarrow \reals $ be a cost function over dual-arm paths.

% \vspace{-.1in}
{\definition [Optimal Dual-arm Rearrangement] Given arms $\arm^1$, $\arm^2$ and objects $\objectset$ to be moved from initial arrangement $ \ainit \in \Afree$ to target arrangement $ \atarget \in \Afree $, the optimal dual-arm rearrangement problem asks for a dual-arm path $D^* \in \mathcal{D}$, which satisfies the following constraint:

% \vspace{-.15in} 
\begin{equation}
% D^* =  (\pi^{*1}, \pi^{*2}) \ |\ \arrangement(\ainit, D^*) = \atarget \textrm{ and } \pi^{*i} \in \cfree^i(\pi^{*j}) \vspace{-.05in}
\label{eq:dualarm_constraint}
\end{equation}
\noindent and optimizes a cost function: $D^* = \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} } \ \cost(D).$}

@@

% \vspace{-.15in}
{\assumption [Monotonicity] There are dual-arm paths $D = (\pi^1,\pi^2)$ that satisfy Eq. \ref{eq:dualarm_constraint}, where each object $ \object_i \in \objectset $ appears once in $\moveset(\pi^1)$ or $ \moveset(\pi^2)$.}

@@

% \vspace{-.1in}
{\assumption [Synchronicity] Consider dual-arm paths, which can be decomposed into a sequence of simultaneous transfers and moves for both arms:
% \vspace{-.1in}
\begin{equation}
D=\left(T(\pi^1_1,\pi^2_1),M(\pi^1_{1\rightarrow 2},\pi^2_{1\rightarrow 2}), \ldots , M(\pi^1_{\ell-1\rightarrow \ell},\pi^2_{\ell-1\rightarrow \ell}), T(\pi^1_\ell,\pi^2_\ell)\right).
% \vspace{-.05in}
\label{eq:synchronicity}
\end{equation}}
\noindent For simplicity, Eq.~\ref{eq:synchronicity} does not include an initial move from $q^k_{\rm safe} \in \cfree^k$ and a final move back to $q^k_{\rm safe}$. An odd number of objects can also be easily handled. Then, the sequence of object pairs moved during a dual-arm path as in Eq. \ref{eq:synchronicity} is: 
% \vspace{-.1in} 
% $$ \scoma(D) = \left(  \coma_i = (\object_i^1,\object_i^2) \ |\ i,j\in [1,\cdots,\ell], \bigcup_i (\object_i^1 \cup \object_i^2) = \objectset, \object_i^1 \cap \object_j^1 = \object_i^2 \cap \object_j^2 = \emptyset \right). \vspace{-.15in}$$
$$ \scoma(D) = \left(  \coma_i = (\object_i^1,\object_i^2) \ |\ i,j\in [1\cdots \ell], \bigcup_i (\object_i^1 \cup \object_i^2) = \objectset, \forall k,k'\in[1,2], \object_i^k \neq \object_j^{k'} \right). $$

@@

% \vspace{-.1in}
{\assumption [Object Non-Interactivity] There are collision-free transfers $T(\coma_i)$ and moves $M(\coma_{i\rightarrow i^{\prime}})$ regardless of the object poses in $\ainit$ and $\atarget$.}
\commentadd{This entails that there is no interaction between the $n$ resting objects and the arms during transits. Similarly, there are no interactions between the arm-object system and the $n-2$ resting objects during the transfers. Collisions involving the arms, static obstacles and picked objects are always considered.}
\commentdel{
This assumption is valid in tabletop setups where the arms can raise the picked objects above the resting surface. 
% Furthermore, this assumption implies that transfers and moves involving object poses in $\ainit, \atarget$ are always feasible and the challenge is deciding the appropriate sequence of object-to-arm assignments.
This assumption lets the study focus on the challenge of deciding the appropriate sequence of object-to-arm assignments.
}

The metric this work focuses on relates to makespan and minimizes the sum of the longest distances traveled by the arms in each synchronized operation. Let $ \| \pi^k \| $ denote the Euclidean arc length in $\cfree^k  \subset \reals^d$ of path $ \pi^k $. Then, for transfers $\cost( T(\pi^1_i,\pi^2_i) ) = \max\{ \|\pi^1_i\|, \|\pi^2_i\| \}$. Similarly, $\cost( M(\pi^1_{i\rightarrow i^{\prime}},\pi^2_{i\rightarrow i^{\prime}}) ) = \max\{ \|\pi^1_{i\rightarrow i'}\|, \|\pi^2_{i\rightarrow i'}\| \}$. Then, over the entire dual-arm path $ \D $ define:
% \vspace{-.15in}
\begin{equation}
\cost(\D) 
% = \cost_{ T} + \cost_{ M} 
= \sum_{i=1}^{\ell}   \cost(T(\coma_i))   + \sum_{i=1}^{\ell-1}   \cost(M(\coma_{i\rightarrow i+1})). 
% \vspace{-.1in}
\label{eq:cost_function}
\end{equation}
Note that the \textit{transfer} costs do not depend on the order with which the objects are moved but only on the assignment of objects to arms. The \textit{transit} costs arise out of the specific ordering in $ \scoma(D)$. 
Then, for the setup of Definition 1 and under Assumptions 1-3, the problem is to compute the optimal sequence of object pairs $\scoma^*$ so that $D(\scoma^*)$ satisfies Eq.~\ref{eq:dualarm_constraint} and minimizes the cost of Eq.~\ref{eq:cost_function}.

@@

\commentadd{
\noindent \textbf{Note on Assumptions:} This work restricts the study to a class of monotone problems that relate to a range of industrial packing and stowing applications. The monotonicity assumption is often used in manageable variants of well-studied problems~\cite{Wilson:1994fk,Halperin:2000uq}. A monotone solution also implies that every object's start and target is reachable by at least one arm. 
\cameraready{
Objects do not need to be in the commonly reachable workspace as long as the problem is monotone and solvable. Section~\ref{sec:integration} discusses a {\tt NO\_ACT} task that can deal with unbalanced object assignments between two arms. 
}

### 2019-06-03 09_discussion.tex
tase initial update

The current work demonstrates the underlying structure of synchronized dual-arm rearrangement and proposes an \milp formulation, as well as a scalable algorithm \algo that provides fast, high quality solutions. Existing efficient solvers for reductions of the dual-arm problem made \algo effective. Future work will attempt to explore the $k-$arm case and instances of non-monotone rearrangement. The incorporation of manipulation and regrasp reasoning can extend these methods to more cluttered domains.

>>>>

The current work demonstrates the underlying structure of synchronized dual-arm rearrangement and proposes an \milp formulation, as well as a scalable algorithm \algo that provides fast, high quality solutions. Existing efficient solvers for reductions of the dual-arm problem made \algo effective. 
\cameraready
{
Future work will attempt to explore the $k-$arm case. The matching sub-problem ceases to have effective solvers for $k>2$, and heuristics might need to be considered for feasible solutions. Regrasp reasoning can extend this work to non-monotone problem instances. The incorporation of manipulation and grasp reasoning can apply such solvers to more cluttered environments.
}

### 2019-06-03 10_appendix.tex
tase initial update

>>>>

\subsection{Discrete Reachability Benchmark}
In this benchmark, two Kuka arms are placed opposite a target arrangement table. The initial poses of the objects are set to be on opposite ends of the arms, as demonstrated in the image. The purpose of this study is to see the effects of general divided workspaces where both the initial and target poses are not in the region of common reachability of the arms. This is indeed a simpler problem for the coordinated methods, but proves challenging to the naive random split strategy.

\begin{figure}
	\centering
	\includegraphics[width=5.3in]{figures/reachability}
	\includegraphics[width=5.3in]{figures/results/5_kuka_lazy_ms_success.png}
	\includegraphics[width=5.3in]{figures/results/5_kuka_lazy_ms_cost.png}
	\includegraphics[width=5.3in]{figures/results/5_kuka_lazy_ms_time.png}
	\caption{The reachability benchmark}
	\label{fig:reachability_benchmark}
%     \vspace{-.3in}
\end{figure}
